oREVIRT analysis

### 2022-11-07 analysis/irt_analysis.Rmd
prep dif run
push DIF results

>>>>

```{r}
dif_sex <- as_draws_df(irt1_dif_sex_sel)%>%
  select(b_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val = b_Intercept + value)%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  left_join(aoa%>%rename(item = targetWord))

saveRDS(dif_sex, "../saves/model_params_irt1_dif_sex.rds")

dif_sex <- readRDS("../saves/model_params_irt1_dif_sex.rds")

ggplot(dif_sex,aes(reorder(item, -aoa_german_comb), mode, ymin = lci, ymax = uci)) +
	geom_pointrange(aes(col = sex), position = position_dodge(width = .5)) +
	coord_flip() +
  scale_color_colorblind(labels = c("male","female"))+
	labs(x = "Item")+
  theme_minimal()
```

```{r}
params_sex_p <- dif_sex%>%
  select(-uci, -lci)%>%
  pivot_wider(names_from = sex, values_from = mode)%>%
  mutate(sex_dif = f - m)%>%
  ungroup()%>%
  mutate(sd = sd(sex_dif), 
         cut_low = mean(sex_dif)-2*sd,
         cut_high = mean(sex_dif)+2*sd)%>%
  mutate(ex = ifelse(sex_dif >cut_high | sex_dif < cut_low, "out", "in"))

ggplot(params_sex_p, aes(x = sex_dif, label = item, y = reorder(item, abs(sex_dif)), col = ex))+
  geom_vline(aes(xintercept = cut_low), lty = 3, alpha = .75)+
  geom_vline(aes(xintercept = cut_high), lty = 3, alpha = .75)+
  geom_point(alpha = .5)+
  scale_color_manual(values = c("black", "firebrick"))+
  guides(col = "none")+
  labs(x = "Difference between estimates (female - male)", y = "Target word")+
  theme_few()
```
